A unified model for parsing and sentence understanding

### 2016-03-13 writing/hard_stack_paper/paper.tex
shift-reduce -> push-merge

\newcommand{\shift}{\textsc{shift}}
\newcommand{\reduce}{\textsc{reduce}}

@@

\paragraph{The size of the stack}
The size of the stack should be $N$ for sentences of $N$ words, in case the first reduce merges the final two words. The size of the buffer should be $N$.

@@

Cropping necessarily discards information, but if done properly, it is nonetheless possible to learn good representations for cropped sentences. When a transition sequence is cropped, the number of removed \shift~transitions is tracked, and an equal number of word tokens is removed from the tail (left) end of the buffer. This makes it possible for a transition sequence to begin with a \reduce~transition, or to otherwise use a \reduce~transition on a stack that does not have two elements to reduce. In this instance, we simply feed the composition function one or more zero vectors, which represent nonexistent stack elements. If the composition learns to interpret these zero vectors properly, they can be taken to be unknown or incomplete nodes in an otherwise complete tree that is constructed according to the intended parse structure. \todo{[SB] Make a figure showing the results of cropping if there's room.}

>>>>

\newcommand{\shift}{\textsc{push}}
\newcommand{\reduce}{\textsc{merge}}

@@

\paragraph{The size of the stack}
The size of the stack should be $N$ for sentences of $N$ words, in case the first \reduce~operation merges the final two words. The size of the buffer should be $N$.

@@

Cropping necessarily discards information, but if done properly, it is nonetheless possible to learn good representations for cropped sentences. When a transition sequence is cropped, the number of removed \shift~transitions is tracked, and an equal number of word tokens is removed from the tail (left) end of the buffer. This makes it possible for a transition sequence to begin with a \reduce~transition, or to otherwise use a \reduce~transition on a stack that does not have two elements to merge. In this instance, we simply feed the composition function one or more zero vectors, which represent nonexistent stack elements. If the composition learns to interpret these zero vectors properly, they can be taken to be unknown or incomplete nodes in an otherwise complete tree that is constructed according to the intended parse structure. \todo{[SB] Make a figure showing the results of cropping if there's room.}
